A Monte Carlo Synthetic Acceleration Method for Solving the Thermal Radiation Diffusion Equation\tnoteref{label1}

### 2012-07-09 doc/jcomp2012/jcomp2012.tex
Fixed a few typos in the jcomp paper

  %% use the tnoteref command within \title for footnotes;
  %% use the tnotetext command for the associated footnote;
  %% use the fnref command within \author or \address for footnotes;
  %% use the fntext command for the associated footnote;
  %% use the corref command within \author for corresponding author footnotes;
  %% use the cortext command for the associated footnote;
  %% use the ead command for the email address,
  %% and the form \ead[url] for the home page:
  %%
  \title{Title\tnoteref{label1}}
  \tnotetext[label1]{}
  \author{Name\corref{cor1}\fnref{label2}}
  \ead{email address}
  \ead[url]{home page}
  \fntext[label2]{}
  \cortext[cor1]{}
  \address{Address\fnref{label3}}
  \fntext[label3]{}

  \title{A Monte Carlo Synthetic Acceleration Method for Solving the
    Thermal Radiation Diffusion Equation}

  %% use optional labels to link authors explicitly to addresses:
  %% \author[label1,label2]{<author name>}
  %% \address[label1]{<address>}
  %% \address[label2]{<address>}

  \author{}

  \address{}

@@

  %%---------------------------------------------------------------------------%%
  \begin{keyword}
    %% keywords here, in the form: keyword \sep keyword

    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)

@@

\begin{table}[htpb!]
  \begin{center}
    \begin{tabular}{lrr}\hline\hline
      \multicolumn{1}{c}{Method} & 
      \multicolumn{1}{c}{Max Iterations} & 
      \multicolumn{1}{c}{Relative CPU Time}\\\hline\hline
      %%
      PCG & 11 & 1.11 \\
      %%
      PFIX & 11 & 1.42 \\
      %%
      MCSA & 11 & 1.0 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{Comparison of solution methods for the Marshak problem. All
    methods were run with a stopping criterion of $\sn{1}{-8}$.  The
    MCSA method used $N_p=10$ and $W_c = \sn{1}{-4}$.  The CPU time is
    measured relative to the MCSA method, which required 72.6 s on a
    3.6~GHz Xeon.}
  \label{tab:marshak_comparision}
\end{table}

@@

Table~\ref{tab:multimat_comparision} shows the timing results for the
multi-material problem using PCG, PFIX, and MCSA.  The results
correspond roughly with the results from the Marshak problem.  The
MCSA is marginally faster than PCG and 43\% faster than PFIX.

\begin{table}[htpb!]
  \begin{center}
    \begin{tabular}{lrr}\hline\hline
      \multicolumn{1}{c}{Method} & 
      \multicolumn{1}{c}{Max Iterations} & 
      \multicolumn{1}{c}{Relative CPU Time}\\\hline\hline
      %%
      PCG & 18 & 1.03 \\
      %%
      PFIX & 38 & 1.43 \\
      %%
      MCSA & 20 & 1.0 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{
    Comparison of solution methods for the multi-material problem. All
    methods were run with a stopping criterion of $\sn{1}{-8}$.  The
    MCSA method used $N_p=1000$ and $W_c = \sn{1}{-3}$.  The problem
    was run to an elapsed time of 10~sh.  The MCSA method required 3.4
    hours on a 3.6~GHz Xeon.}
  \label{tab:multimat_comparision}
\end{table}

>>>>

  \title{A Monte Carlo Synthetic Acceleration Method for Solving the
    Thermal Radiation Diffusion Equation\tnoteref{label1}}
  \tnotetext[label1]{}

  \author[ornl]{Thomas M. Evans\corref{cor1}\fnref{fn1}}
  \ead{evanstm@ornlgov}
  \ead[url]{www.ornl.gov}
  \cortext[cor1]{Corresponding Author}

  \author[ornl]{Scott W. Mosher\fnref{fn1}}
  \ead{moshersw@ornl.gov}

  \author[wisc]{Stuart R. Slattery\fnref{fn2}}
  \ead{sslattery@wisc.edu}
  \ead[url]{www.wisc.edu}

  \fntext[fn1]{Radiation Transport Group, Reactor and Nuclear Systems
    Division} 
  \fntext[fn2]{Department of Engineering Physics, College of Engineering}

  \address[ornl]{Oak Ridge National Laboratory, 
    1 Bethel Valley Rd., Oak Ridge, TN 378131 U.S.A.}
  \address[wisc]{University of Wisconsin-Madison, 1500 Engineering
    Dr., Madison, WI 53716, U.S.A.}

@@

  %%---------------------------------------------------------------------------%%
  \begin{keyword}
    %% keywords here, in the form: keyword \sep keyword
    radiation diffusion \sep Monte Carlo \sep sparse matrix systems
    %% MSC codes here, in the form: \MSC code \sep code
    %% or \MSC[2008] code \sep code (2000 is the default)

@@

\begin{table}[htpb!]
  \begin{center}
    \begin{tabular}{lrr}\hline\hline
      \multicolumn{1}{c}{Method} & 
      \multicolumn{1}{c}{Max Iterations} & 
      \multicolumn{1}{c}{Relative CPU Time}\\\hline\hline
      %%
      PCG & 11 & 1.11 \\
      %%
      PFIX & 11 & 1.42 \\
      %%
      MCSA & 11 & 1.0 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{Comparison of solution methods for the Marshak problem. All
    methods were run with a stopping criterion of $\sn{1}{-8}$.  The
    MCSA method used $N_p=10$ and $W_c = \sn{1}{-4}$.  The CPU time is
    measured relative to the MCSA method, which required 72.6 s on a
    3.6~GHz Xeon.}
  \label{tab:marshak_comparison}
\end{table}

@@

Table~\ref{tab:multimat_comparison} shows the timing results for the
multi-material problem using PCG, PFIX, and MCSA.  The results
correspond roughly with the results from the Marshak problem.  The
MCSA is marginally faster than PCG and 43\% faster than PFIX.

\begin{table}[htpb!]
  \begin{center}
    \begin{tabular}{lrr}\hline\hline
      \multicolumn{1}{c}{Method} & 
      \multicolumn{1}{c}{Max Iterations} & 
      \multicolumn{1}{c}{Relative CPU Time}\\\hline\hline
      %%
      PCG & 18 & 1.03 \\
      %%
      PFIX & 38 & 1.43 \\
      %%
      MCSA & 20 & 1.0 \\
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{
    Comparison of solution methods for the multi-material problem. All
    methods were run with a stopping criterion of $\sn{1}{-8}$.  The
    MCSA method used $N_p=1000$ and $W_c = \sn{1}{-3}$.  The problem
    was run to an elapsed time of 10~sh.  The MCSA method required 3.4
    hours on a 3.6~GHz Xeon.}
  \label{tab:multimat_comparison}
\end{table}
